---
title: "Plot spatial data with leaflet "
author: "MM2"
date: "January, 2018"
output: 
  html_document:
        toc: true
        theme: united
runtime: shiny
---
```{r,message=FALSE,error=FALSE,warning=FALSE,echo=FALSE}
rm(list=ls())

# set the working directory
wd = "Q:\\portfolios\\daastrat\\daastrat1m4\\Rcode\\Testing"
wd = "F:\\leaflet mapping\\Testing"
setwd(wd)
```

# The required libraries
```{r,message=FALSE,error=FALSE,warning=FALSE}
library(sp)
library(rgdal) # reading spatial files into R
library(geosphere)
library(rgeos)
library(leaflet)
library(htmlwidgets) # Saving leaflet output as html
library(webshot)
library(RColorBrewer)
library(raster)
library(rlist) # save a list to a file and read that in again 
```

# Read in the shape data
A powerful way for reading in spatial data into `R` is `readOGR` from the package `rgdal`. `readOGR` reads `*.shp` shape file along with other files (extensions: `dbf`, `shp`, `shx`) in the same folder simultaneously.  It has two required parameters `dsn` and `layer`. The first argument is the path of the shapefile whereas the second argument is the layer name without an extension.

```{r,message=FALSE,warning=FALSE}
WA = readOGR(wd, "WA_MeshBlocks")
Midland = readOGR(wd, "MidlandShops") 
```

The shapefile is read as a `SpatialPolygonsDataFrame` object, (multi)polygons as well as a data frame (nongeographic attribute data) where each row stores the attributes.

```{r}
class(WA);class(Midland)
```

The projection information for this spatial object is:

```{r}
proj4string(WA);proj4string(Midland)
```

# Mapping with Leaflet
 Firstly, the dataset is cut down including both data and polygons to speed up mapping and loading process in `leaflet`.

```{r}
sub_WA = subset(WA, gcc_name16 == "Greater Perth")
sub_WA2 = subset(WA,sa4_name16 == levels(WA@data$sa4_name16)[grep("Perth",levels(WA@data$sa4_name16))])
WA_Midland = subset(WA,sa2_name16 == levels(WA@data$sa2_name16)[grep("Midland",levels(WA@data$sa2_name16))])
```